Distributed Version Control Systems

### 2010-06-07 laarsample.tex
Agregado comentario sobre mercurial
Agregado abstract, y en base a este reescrita parte de la introduccion

\abstract
Estas instrucciones se presentan para ayudar a los autores a preparar su trabajo en el formato definitivo correspondiente a la materia Arquitecturas de Proyectos de IT. El resumen no debe exceder las 200 palabras.
\endabstract

@@

Most software projects use Version Control Systems (VCS) to manage revisions
of source code. 
Version Control Systems traditionally track the whole history of the
source code in a central server that everyone that can access. 
%This central server contains all the changes and branches of the code and 
%the users that can read the versions or commit changes have to connect 
%to this repository. 
Users need to access this central server to work with their VCS.
A modern, different approach of doing revision control is using a \emph{Distributed} Version Control System (DVCS).
In these systems, there is no central server that contains the history and tracks changes,
instead everyone has a copy of the full repository with the complete history.
Given the lack of a centralized server they are also called De-centralized Version Control Systems.

In this paper we're going explain what DVCS are, based on the distributed system Git, 
and compare them to centralized Version Control Systems,
highlighting the differences, advantages and disadvantages of both approachs in various 
contexts, in a both a conceptual level, and a practical level of actual VCS; ultimately 
evaluating when to use or not Distributed Version Control Systems.

@@

%----------------------------------------------------------------------

>>>>

\abstract
%Estas instrucciones se presentan para ayudar a los autores a preparar su trabajo en el formato definitivo 
%correspondiente a la materia Arquitecturas de Proyectos de IT. El resumen no debe exceder las 200 palabras.
%
%
Distributed Version Control Systems, as opposed to Centralized Version Control Systems, 
are increasingly popular, being today a serious option in the election of a Version
Control System.
The goal of this paper is to explain what DVCS are, based on the distributed system Git, 
and compare them to Centralized Version Control Systems,
highlighting the differences, advantages and disadvantages of both approachs in various 
contexts, in a both a conceptual level, and a practical level of actual VCS; ultimately 
evaluating when to use or not Distributed Version Control Systems. 
%aprox. 60 palabras fue eso
\endabstract

@@

Most software projects use Version Control Systems (VCS) to manage revisions
of source code. 
Version Control Systems traditionally track the whole history of the
source code in a central server that everyone that can access. 
Users need to access this central server to work with their VCS.
A modern, different approach of doing revision control is using a \emph{Distributed} Version Control System (DVCS).
In these systems, there is no central server that contains the history and tracks changes,
instead everyone has a copy of the full repository with the complete history.
Given the lack of a centralized server they are also called De-centralized Version Control Systems.

As stated in the abstract, we're going to do an overview of DVCS and comparison, based on the DVCS Git. 
First we're going to have a quick look to the history of DVCS. Then there is a review of the overall architecture of DVCS, and then a comparison to centralized version control systems. Some workflows enabled by the use of Distributed Version Control Systems are described, and finally a general evaluation of Git, DVCS in general, and whether it is or not a good idea to switch to them.

@@

Mercurial has similar tools, incluing hg-subversion to interact with svn repositories, and Tortoise-Hg which is
the equivalent of Tortoise-Git.
%----------------------------------------------------------------------
